White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-09-19 papers/wdmerger_II/paper.tex
Add preliminary data for spatial resolution dependence

%TODO: update the above with more recent data.

@@

>>>>

@@

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.425]{{{plots/amr}}}
  \caption{Nickel production as a function of the simulation resolution. The solid
           black curve connects the points at uniform resolution. For each uniform
           resolution simulation, we include additional simulations using the adaptive
           mesh refinement criterion described in \autoref{sec:unstable_burning}.
           The horizontal axis is the effective number of zones per dimension on the
           finest level, which is the number of zones per dimension that would exist
           if the finest resolution was uniformly applied on the grid.
           \label{fig:amr}}
\end{figure}
